\documentclass[12pt, a4paper]{article}
\usepackage{geometry}
\geometry{margin=0.5in}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\renewcommand{\familydefault}{\sfdefault}

\newcommand{\speak}[2]{\begin{description}\item[\textbf{#1}]#2\end{description}}

\begin{document}

\centering

{\huge General Members Assembly - Minutes}

{\large June 13th 2022, 19:30}

\vspace{40pt}

\raggedright

{\large Participants}

Emily Demmer

Annalena Schröder

Ilse Jonker

Rick Roodbergen

Anne-Lin Langbroek

Santiago Gomez (Santi)

Myrthe de Haan

Oscar Paananen

Martin Karkossa (Marty)

Carolina Spanner

Roos Slijfer

\vspace{\baselineskip}
{\large Present by Proxy}

Mads Madsen proxies Roos Slijfer

Ilse Jonker proxies Myrthe de Haan

Jorrit Grob proxies Oscar Paananen

Casper Wijtsma proxies Rick Roodbergen

Charlotte Sievers proxies Annalena Schröder

Aleksandra Rodak proxies Annalena Schröder

Elmar Klein proxies Myrthe de Haan

\vspace{50pt}

\tableofcontents

\pagebreak

\section{Opening}

\textit{The assembly is openened at 20:48.}

\section{Increase in Yearly Contribution}

\textit{The proposal for increase in contribution is presented by Carolina Spanner. Only questions and answers are shown here.}

\speak{Roos}{Why are we making that big of a loss this year in contrast with the other years?}

\speak{Anne-Lin}{We made the biggest loss last year [not this year], but we have been making a loss the last few years.}

\dots

\speak{Annalena}{There was something about the Gladiool loan, so 1200 euros are costs, but also fixed revenue 1200, and also something about 3000 euros that we lost to the Gladiool, what happened there?}

\speak{Carolina}{This was explained during the GMA in October, but there were no questions so there was no deep dive. A few years back, the Gladiool needed a loan for the bar or something. We gave them a 3000 euro loan. Parabool gave 7000 euros. This was under the agreement that we would get it back in x number of years, and they would apply for the BOSA subsidy. However their secretary in that time should have applied for the BOSA subsidy, but that didn't happen. So we won't be getting that subsidy anymore, because the time has already passed. The president of the Gladiool called multiple times to see if it is still possible, but they were too late with it. That's why the Gladiool sent a letter in October to explain this, and that they cannot give this money back anymore.}

\speak{Annalena}{So the 1200 is something different?}

\speak{Anne-Lin}{In order to rebalance this in our books, we are paying the Gladiool 100 euros a month, but they are also paying us back 100 euros, to "pay back" the loan. So according to the books, we are getting back the loan, but we are also paying for it.}

\dots

\speak{Oscar}{Are we still giving clinics? I haven't heard anything about clinics in a while, and I remember that used to be pretty solid income.}

\speak{Carolina}{There is a special clinics groupchat where new clinics are posted. But it has not been as much as previous years.}

\speak{Oscar}{I remember when Maarten was the clinic commissioner, I told him I was always available. I am always willing to help out.}

\dots

\speak{Annalena}{In the financial documents, there was something about a picnic table for 300 euros, why did the board decide to buy the table for 300 euros when we are already struggling?}

\speak{Carolina}{It was not our old picnic table, it was the Parabool's. They received it as a gift from alumni members. During the KEI party in August, the picnic table was broken. Basti had KEI reimburse us for the table for 300 euros. We asked de Parabool if we should just keep the money, but de Parabool said that they wanted a new picnic table since it was a gift.}

\dots

\speak{Myrthe}{In contrast to the last GMA, when we didn't vote in favor of this proposal, we asked what would be a reasonable amount and we gave like different suggestions you guys would look at, did you take that into consideration? Also, I didn't read the whole spreadsheet because I'm not good at finance, and I know it's a bad situation and we don't have the money to spare. It's a bit sad that there wasn't any compromise possible.}

\speak{Carolina}{We did look into it, this [calculation spreadsheet] is what was made by Anne-Lin as well to help understand our math, and [the suggestions] will not give us the cushion we need.}

\speak{Anne-Lin}{If you put the 150 down and 90 for half-year, then the difference in fixed costs still is 300 euros. Then if you put 120 in there and 72 for half-year, then the difference in fixed costs is 4200, which is still a lot that needs to be bridged with variable costs \& incomes. When I made this, in our bank account we had only 2800 euros. With that we won't even last a year, it will be gone within a year.}

\speak{Myrthe}{So 140, 145 is also not possible?}

\speak{Anne-Lin}{No.}

\dots

\speak{Ilse}{If I understand correctly, if we all pay 150 euros and we all stay, then we are still 3000 euros in the red for next year?}

\speak{Anne-Lin}{Yes throughout the whole year, we'd be making a loss of 3000 euros.}

\speak{Ilse}{So since we don't have a financial cushion, we will [go bankrupt] within the next year?}

\speak{Anne-Lin}{Yes, so we have to figure out more ways to make money, we are looking into that like for example fundraisers that we did during gamedays, like the BBQ during the Men's gameday with 200 euros. Bake sale made 124 euros this year, and also consumptions during the BBQ. We want to get more of those kind of things to bridge the 3000 next year.}

\dots

\speak{Myrthe}{Did you also make a calculation with how many people are leaving, and maybe an estimate on how many people are joining next year? Do you have any idea how many people are leaving?}

\speak{Carolina}{They have until the first of August to do so, so we don't know yet.}

\speak{Myrthe}{I don't need to know, but it will matter for how many times we are getting the 150.}

\speak{Anne-Lin}{We are expecting more people because of the basisbeurs, and there is a trial going on with MBO students.}

\speak{Emily}{For the women's team, more people are staying this year than last year.}

\dots

\speak{Rick}{I had sent in a question beforehand, that was not answered yet regarding club house rent and the contract details. When can we get rid of the club house if necessary because it's minus 10,000 a year. If necessary, when can we legally stop the rent or quit the rent. Is there any options there?}

\speak{Carolina}{The contract does exist, but we weren't able to get to it yet, so we are not sure if there is an escape clause.}

\speak{Rick}{But there is a fixed time, right?}

\speak{Marty}{It's 15 years that we're allowed to have the club house here, and 15 years is also the time that we planned to pay off our loans. So the whole thing is set up for 15 years. After that time, the loan will be paid off and it will be a whole lot cheaper. So we have about 13 years left.}

\dots

\speak{Annalena}{This is about contribution only, not about renting club gear, correct?}

\speak{Carolina}{Correct.}

\dots

\speak{Marty}{I have a comment. I got many messages from people, asking if we can't make money in other ways rather than raising contribution. That gave me the impression that maybe we haven't been communicating very well about what we're trying to do and what our options are, because we have been trying in many ways. There were a couple good suggestions to also look into in the future, but also things like sponsorships, giving more clinics, renting out the club house more, and these are all things we've been working on. We're hoping to get a new physio sponsor soon. For reference, we had a physio sponsor once and it was 400 euros and that was very generous, most sponors would not have given that. Also back then we had 80 members. So I would not bank on a physio sponsor. They would give us at most 200 euros, if we even get the sponsors.}

\speak{Oscar}{Was that Construction?}

\speak{Marty}{No, it was Noorderbad. But yes, getting sponsors requires a lot of work, we need to offer something in return, like doing a lot of promotion which requires an active promotion committee. Same with renting out the clubhouse, you need to find clubs that want to rent the clubhouse, which is also hard because we're not really allowed to advertise to other clubs. And then we also need people to stand behind the bar so we need volunteers. Same thing for clincs, we need to talk to the schools, and then we need to find volunteers to give the clinics. So all of this requires volunteer work, but we don't know how many people are going to be in the board next year, we don't know how many people are going to be active in committees next year, all we know is this year and last year the board was not completely filled, not all committees were fully filled, so we shouldn't bank on extra income sources that require volunteer work. If it does go really well, and we make like 3000 in the first clinic season, then we can always come together and vote again to lower the contribution. But until we know that for certain, we should not take risks and rely on theoretical money.}

\textit{Increase in member contribution accepted.}

\section{Closing}

\textit{Assembly closed at 21:20.}

\end{document}